---
title: "Via"
author: "Aadish Chopra"
date: "December 20, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

# Analysis done for Via


```{r setup, include=FALSE, cache=TRUE,autodep=TRUE,warning=FALSE,message=FALSE,results='asis'}
knitr::opts_chunk$set(echo = TRUE)
```

Importing the dataset in  R

## R Markdown
```{r}
library(readxl)
Via_ <- read_excel("D:/UIC/Interviews/Via .xlsx", 
    col_types = c("text", "text", "date"))
Via_<-Via_[complete.cases(Via_),]

```


###Exploratory Analysis

Calculating how many agents are there ?

```{r  }
library(knitr)
No_of_accounts_manager<-length(unique(Via_$`Account manager`))
Names_of_accounts_manager<-as.data.frame(unique(Via_$`Account manager`))
colnames(Names_of_accounts_manager)<-"Names"
kable(Names_of_accounts_manager)

```

Calculating how many different clients are there ?

```{r eval=FALSE}

No_of_unique_clients<-length(unique((Via_$`Client Name`)))
No_of_unique_clients


```

We can see that there are 4 different accounts manager and 25 different clients

Now we will see how many account manager have handled different clients

```{r warning=FALSE,message=FALSE}
library("ggplot2")
g1<-ggplot(data=Via_)+
geom_bar(aes(x=Via_$`Account manager`,fill=Via_$`Client Name`))

plot(g1)



```




```{r}
library("dplyr")
#??? scope of improvement of code ???
 
Milan_Crona<-Via_[Via_$`Account manager`==Names_of_accounts_manager[1,],]
  
FMilanCrona<-as.data.frame(sort(table(Milan_Crona$`Client Name`),decreasing=TRUE))
colnames(FMilanCrona)<-"MCClient Name"
    
Aidan_Pouros<-Via_[Via_$`Account manager`==Names_of_accounts_manager[2,],]
  
FAidan_Pouros<-as.data.frame(sort(table(Aidan_Pouros$`Client Name`),decreasing=TRUE))
colnames(FAidan_Pouros)<-"APClient Name"

Chauncey_Dach<-Via_[Via_$`Account manager`==Names_of_accounts_manager[3,],]
  
FChauncey_Dach<-as.data.frame(sort(table(Chauncey_Dach$`Client Name`),decreasing=TRUE))
colnames(FChauncey_Dach)<-"CDClient Name"

Rigoberto_White<-Via_[Via_$`Account manager`==Names_of_accounts_manager[4,],]
  
FRigoberto_White<-as.data.frame(sort(table(Rigoberto_White$`Client Name`),decreasing=TRUE))
colnames(FRigoberto_White)<-"RWClient Name"

kable(FMilanCrona)

kable(FAidan_Pouros)

kable(FChauncey_Dach)

kable(FRigoberto_White)

```

From the above tables we can get information such as which client met with which 

```{r warning=FALSE,message=FALSE}

library(lubridate)

Y2013<-(subset(Via_, format(Via_$`Date of Contact`,"%Y")==2013))
Y2014<-(subset(Via_, format(Via_$`Date of Contact`,"%Y")==2014))
Y2015<-(subset(Via_, format(Via_$`Date of Contact`,"%Y")==2015))
Y2016<-(subset(Via_, format(Via_$`Date of Contact`,"%Y")==2016))
Y2017<-(subset(Via_, format(Via_$`Date of Contact`,"%Y")==2016))
  
M2013<-as.data.frame(sort(table(lubridate::month(Y2013$`Date of Contact`)),decreasing = T))

colnames(M2013)<-c("Month","Frequency")
M2014<-as.data.frame(sort(table(lubridate::month(Y2014$`Date of Contact`)),decreasing = T))
colnames(M2014)<-c("Month","Frequency")
M2015<-as.data.frame(sort(table(lubridate::month(Y2015$`Date of Contact`)),decreasing = T))
colnames(M2015)<-c("Month","Frequency")
M2016<-as.data.frame(sort(table(lubridate::month(Y2016$`Date of Contact`)),decreasing = T))
colnames(M2016)<-c("Month","Frequency")
M2017<-as.data.frame(sort(table(lubridate::month(Y2017$`Date of Contact`)),decreasing = T))
colnames(M2017)<-c("Month","Frequency")

kable(M2013)
kable(M2014)
kable(M2015)
kable(M2016)
kable(M2017)

```


#From this we know that most of times agents contacted in the Month of October in all the years







